Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
The last phase

  If we have at least two phases, then we assume that OPT did not pay during that, and the cost of ALG increases at most twofold.
\end{proof}

>>>>

  If we have at least two phases, then we split the cost $\alpha$ charged in the penultimate phase into last two phases, and follow the analysis regarding the unsaturated requests
  This way, the competitive ratio increases at most twofold.
\end{proof}
